---
title: "Chapter 4, 5, 6, and 7 Applications"
output: html_document
---

The "OfficeParks.csv" file contains data (as you saw in Chapter 1) regarding several aspects of health and behavior of the characters in both *The Office (US)* and *Parks and Recreation* television shows. Notably, this is a ficticious data set not supported by NBC.

In the following code chunks, complete each section.

## Import the Data

Import the data (with something like `rio::import()`).

```{r}

```

## Chapter 4

### T-test

Run a t-test with the data. You pick which variables to use.

```{r}

```


### ANOVA

Run an ANOVA with the same model as the t-test above.

```{r}

```

### Linear Regression

Run an linear regression with any of the variables you'd like to.

```{r}

```

## Chapter 5

### Logistic Regression

Run a logistic regression model with any of the predictors but use one of the binary variables for the outcome.

```{r}

```



## Chapter 6

To do this chapter, we need to first reshape the data to make it "tidy." We can do that here with `furniture::long()`.

```{r}

```

No that we have a "tidy" version of the data, we can run the multilevel models below.

### GEE 

Run a GEE model.

```{r}

```


### Mixed Effects Model

Run a mixed effects model.

```{r}

```


## Chapter 7

We can go back to our "untidy" data to run these models.

### Mediation Model

Run a mediation model using either `MarginalMediation` or `lavaan`.

```{r}

```


### Structural Equation Modeling

Run an SEM model using `lavaan`.


```{r}

```


### Machine Learning Techniques

Run any of the machine learning techniques we've learned using the `caret` package.

```{r}

```


